A Study of Common Bug Fix Patterns in Rust

### 2022-11-27 discussion.tex
threats to validity fixed

In our work there are three main threats to internal validity: (1) We use a weighting scheme which is based on a heuristic to give more values to tree elements closer to the leaves. In addition to that, we also manually adjusted the weights of borrow checker related elements to respect the ownership framework's role in Rust, though we recorded their results separate from general results. As this approach is based on intuition, it does not guarantee achieving optimal clusters. (2) The collected commits are the ones that fix a bug in a previously pushed commit. We do not consider the bugs that occur during a commit and also fixed during the same commit. (3) Our code embedding approach is based on the frequency of observed program elements in ASTs, and we use DBSCAN as our clustering algorithm. Other program code embedding methods and clustering algorithms (e.g. SLINK) might output new clusters that our pipeline is unable to find.

A threat to external validity can be the developers reporting the commits as bug fixing commits while they are not really fixing a functionality. Similarly, a commit message might not contain our target keywords while the commit is associated with bug fixing changes.
\todo[inline]{Are internal and external used properly?}

>>>>

In our work there are three main threats to internal validity: (1) We use a weighting scheme which is based on a heuristic to give more values to tree elements closer to the leaves. In addition to that, we also manually adjusted the weights based on our knowledge of Rust. As this approach is based on our own judgement, it does not guarantee achieving optimal clusters. Nevertheless, our weighting scheme can be readjusted to find different patterns, which is why we made our pipeline publicly available. (2) The collected commits are the ones that fix a bug in a previously pushed commit. We do not consider the bugs that occur during a commit and also fixed during the same commit. (3) Our code embedding approach is based on the frequency of observed program elements in ASTs, and we use DBSCAN as our clustering algorithm. Other program code embedding methods and clustering algorithms (e.g. SLINK) might output new clusters that our pipeline is unable to find.

Threats to external validity can be described as: (1) The developers reporting the commits as bug fixing commits while they are not really fixing a functionality. Similarly, a commit message might not contain our target keywords while the commit is associated with bug fixing changes. (2) The selected projects might cause selection bias and therefore we might not have presented patterns that may exist in other projects.
